---
title: 'Homework 4: Odds Ratios and Relative Risk'
subtitle: "STAT 244NF: Infectious Disease Modeling"
author: "YOUR NAME HERE"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

## Instructions:

1. Please replace "YOUR NAME HERE" under author above with your name before you knit your final document for submission.
2. All of your homework needs to be completed in this document, whether it requires R or just typed responses. As we incorporate more statistical computing into the course, it will be important that you are comfortable with R Markdown, so start now. Remember that R Markdown gives us a convenient framework for reproducible statistical reports because it contains a complete record of our analyses and conclusions.
3. You may knit to PDF, HTML, or Word (click on the drop-down menu for Knit to choose the file output type). 
4. Before submitting your work, please make sure the knitted file is well organized, legible, and looks the way you expect!
5. Please include the names of any classmates with whom you worked on this homework, as well as any external resources that you might have used.
6. This homework assignment is **due on Friday, September 24, 2021 and should be submitted to Gradescope**.

- *Collaborators:*

- *External resources:*

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(ggplot2)
```

## Infectious Disease Outbreak

An infectious disease outbreak has been reported. In a population of 1000, epidemiological investigators identified 526 cases of disease and tracked possible exposures, including a winter festival. The data for this outbreak are generated below and saved as `id_outbreak`. 

```{r}
set.seed(12943)
simulation <- rmultinom(n = 1, size = 1000, prob = c(400/1000, 100/1000, 126/1000, 374/1000))

## 0=no, 1=yes
id_outbreak <- data.frame(case=c(rep(1, simulation[1]), rep(0, simulation[2]),
                                 rep(1, simulation[3]), rep(0, simulation[4])),
                          winter_festival=c(rep(1, simulation[1]), rep(1, simulation[2]),
                                            rep(0, simulation[3]), rep(0, simulation[4])))

```

#### Question ID 1. What kind of study would generate these data?


#### Question ID 2. Both relative risk and odds ratio are defined in terms of probabilities related to exposure/non-exposure. What constitutes "exposure" in this study? What about "non-exposure"?


#### Question ID 3. Calculate the following probabilities based on the data in `id_outbreak`.

(a) $P(\text{disease}|\text{exposure})$

```{r}

```

(b) $P(\text{disease}|\text{non-exposure})$

```{r}

```

(c) Calculate the relative risk, the chance that a person who attended the winter festival will develop disease relative to the chance that a person who did not attend the winter festival will develop disease. 

```{r}

```

(d) Calculate the odds ratio associated with this outbreak.

```{r}

```

#### Question ID 4. Poisson regression

(a) Fit a Poisson regression model with only an intercept to these data. Remember to use the `glm` function and to specify `family` argument in the `glm` function as `poisson`. Assign the model fit to `outbreak_pois` and print the summary of the model fit.

```{r}

```

(b) What is the estimate of the intercept? Exponetiate this estimate. How does this compare to the quantities you calculated in Question ID 3? Interpret this value in context.

```{r}

```

(c) Find a 95% confidence interval for the estimate in (b). You can use the `confint` function and exponentiate that interval to get that interval. Please interpret this interval in context.

```{r}

```


#### Question ID 5. Binomial logistic regression

(a) Fit a logistic regression model with only an intercept to these data. Remember to use the `glm` function and to specify `family` argument in the `glm` function as `binomial`. Assign the model fit to `outbreak_pois` and print the summary of the model fit.

```{r}

```

(b) What is the estimate of the intercept? Exponentiate this estimate. 

```{r}

```


(c) Find a 95% confidence interval for the estimate in (b). You can use the `confint` function and exponentiate that interval to get that interval. Please interpret this interval in context.

```{r}

```

(d) Compare the estimates and confidence intervals from the poisson and logistic regression models. How do the relative risk and odds ratios compare in this example?



## NSF Computing Intervention

Please watch the two YouTube tutorials linked in Moodle under the homework for Week 4. Then answer the following questions.

#### Question NSF 1. Which statement about functions is false?

A. Some functions have input values.
B. All functions have return values.
C. A function is a named block of instructions with a particular purpose.

#### Question NSF 2. Consider the following R code, which was used to generate the simulated data in our disease outbreak above: `rbinom(n = N_d, size = 1, prob = N_fest/N_d)`

(a) What are the parameters in that line of code?


(b) What are the arguments in that line of code?


#### Question NSF 3. Are there default values for all the parameters in `rbinom()`? Are there default values for *any* of the parameters in `rbinom()`? If so, which ones?


#### Question NSF 4. Suppose we run the following: `rbinom(N_d, 1, N_fest/N_d)`. What are we relying on for matching arguments to parameters?


#### Question NSF 5. `rbinom(N_d, 1, N_fest/N_d)` and `rbinom(1, N_d, N_fest/N_d)` give different outputs. Why?



#### Question NSF 6. `rbinom(n = N_d, size = 1, prob = N_fest/N_d)` and `rbinom(size = 1, n = N_d, prob = N_fest/N_d)` no not give different outputs. Why?